Late Fusion via Subspace Search with Consistency Preservation

### 2017-03-17 egpaper_for_review.tex
finish iccv

\def\M{\mathcal{M}}
\def\R{{\mathbb R}}
\def\bR{{\bf R}}
\def\U{{\bf U}}
\def\V{{\bf V}}
\def\diag{\mbox{diag}}
\def\bsigma{\mbox{{\boldmath $\sigma$}}}
\def\trsp{{\sf T}}
\def\I{{\bf I}}
\def\0{{\bf 0}}
\def\G{{\bf G}}
\def\grad{{\text{grad}}}
\def\bZ{{\bf Z}}
\def\bfeta{\mbox{{\boldmath $\eta$}}}
\def\mT{{\mathcal T}}

@@

\def\yanred{\textcolor{red}}
\def\yanblue{\textcolor{blue}}
%%%%%

@@

\begin{abstract}
In many real-world applications, data can be represented in multiple ways or multi-view features,
in order to describe various characteristics of data.
In this way, it could often improve the prediction performance by taking advantage of these feature together.
Late fusion, which combines the predictions of multiple features, is a commonly used approach to make the final decision for a test instance.
However, it is ubiquitous that different features would dispute on the data, which results in performance degeneration.
Therefore, there is a requirement of outlier rejection while preserving consistency among different classifier results.
In this paper, we propose an efficient matrix factorization based approach to fuse predictions from multiple sources,
which could avoid the performance degeneration caused by the controversy of multiple features on test data.
Extensive experiments demonstrate that the proposed method is effective to remove outliers and improve fusion performance.

@@

%% late fusion is a common single model -> single feature, 介绍late fusion
Late fusion, a typical approach to obtaining the final decision on testing data, aims to fuse the predictions from different features.
A commonly used method is to learn weights for predictions from various features to combine them, which has a number of variations~\cite{gehler2009feature,xuiccv2013feature,lai2015learning}.
Among these algorithms, multiple kernel learning (MKL)~\cite{lanckriet2004learning,Rakotomamonjy2008Simplemkl} is often used to train such a weighted combination.
However, a single feature may produce corrupted predictions on some data, which likely degenerates performance.
To deal with this issue, therefore, some works formulate it as a robust low-rank matrix recovery problem~\cite{gaoijcai2016robust,ye2012robust} by nuclear norm minimization.
Nevertheless, nuclear norm minimization applied in these works requires singular value decompositions (SVDs), which would be computationally unaffordable for large matrices.

\begin{figure}[!t]
\begin{center}
\includegraphics[width=0.48\textwidth]{resource/frame_work.pdf}
\end{center}
\caption{Framework of our late fusion algorithm.
In this example, there are 10 instances 3 classifiers and 3 classes.
Predictions of each classifier are converted to a binary indicator matrix,
denoted by $L_1$, $L_2$ and $L_3$.
Let $L = [L_1, L_2, L_3]$ be the label matrix.
Our algorithm detects and removes the outliers on $L$ and then recover the underlying low-rank subspace of $L$ as the prediction for testing instances.
We finally apply a post-processing method to generate the fused results.
%First, there are $\calC=3$ classifiers' results for $n=10$ instances.
%Each of them are converted into ``binary'' indicators from the soft prediction results, as $L = [L_1, L_2, L_3]$.
%Then, our ALM-based optimization process the binary indicator matrix into a recovered matrix $X$,
%which can be treated as soft prediction scores for testing instances.
%Finally, the fused prediction results are generated by a post-processing method.
}
\label{fig:framework}
\end{figure}

To prevent from the expensive nuclear norm minimization,
in this paper, we propose a more efficient matrix factorization algorithm to recover the underlying low-rank label matrix.
Particularly, our method searches the solution in a low-rank subspace under a fixed-rank constraint.
As for outlier detection,
we propose to filter out these inconsistent predictions on specific classes of models (See Fig.\ref{fig:framework}.
Notations are introduced shortly.).
\yanred{
The $\ell_{1,2}$ loss preserves the fidelity within each column by $L_2$ loss in the vertical direction and is robust to sparse errors across all the columns by $L_1$ loss in the horizontal direction.
However, the single $L_2$ doesn't have the ability to detect outliers and the single $L_1$ has the instability property.
Based on this observation, we apply this robust $\ell_{1,2}$ loss to remove the outlier columns in the label indicator matrix.
}
Furthermore, most existing matrix factorization optimization methods only consider smooth loss functions, rather than the non-smooth loss.
We thus in particular present an approach based on augmented Lagrangian multiplier (ALM) to extend matrix factorization methods to non-smooth problems.

The main contributions of this work are summarized as below:
\begin{itemize}
  \item We formulate the late fusion problem as a fixed-rank robust matrix recovery problem based on matrix factorization, which intuitively preserves the consistency of predictions from different sources.
  \item We propose an ALM based algorithm to extend existing matrix factorization algorithms from smooth least square loss to non-smooth $\ell_{1,2}$ loss. 
  %\item Our proposed algorithm is more efficient than most state-of-the-art late fusion methods.
  %It is capable of handling large scale problems.
  \item Empirical studies show significantly improvement of our proposed method compared to existing late fusion algorithms.
\end{itemize}

@@

MKL based method is a simple but efficient way to combine different features for multi-model fusion,
and many improved algorithms have been proposed by introducing more constraint, boosting methods and other optimization.
In~\cite{vedaldi2009multiple}, the authors use MKL to learn an optimal combination of exponential ${\chi}^2$ kernels capturing a different feature channel.
In~\cite{gehler2009feature}, boosting approaches are proposed to ensemble different features, which learns the correct weighting of multiple predicted confidence scores from different models.
In~\cite{natarajan2012multimodal}, the authors propose a two-step strategy employing MKL and late score fusion methods to combine diverse features, specifically on event detection tasks.
In~\cite{lai2015learning}, a sample specific late fusion based on graph Laplacian with RankSVM style constraints is proposed,
which learns sample specific fusion weights by diffusing the information from labeled samples to the unlabeled one.
In~\cite{xuiccv2013feature}, a optimization algorithm are proposed to combine diverse decision values,
which learns the weights, thresholding and smoothing parameters in a joint framework.
However, all these MKL based fusion methods or others only learn weights to combine different basic models, which do not consider the outlier rejection in the fusion process specifically.

%Our proposed late fusion algorithm is based on matrix factorization,
%which has attracted increasing attention recently.
Matrix factorization has attracted increasing attention recently.
Many manifold optimization algorithms on matrix factorization have been proposed by exploiting the manifold geometry in a subspace.
Based on manifold optimization, fixed-rank matrices are supposed to belong to a smooth matrix manifold~\cite{Absil2008OAMM,vandereycken2013lowrank}.
In~\cite{vandereycken2013lowrank}, the authors propose a low-rank geometric conjugate gradient (LRGeomCG) method.
In~\cite{rtrmc2011boumal}, first- and second-order Riemannian trust-region methods are applied to solve the low-rank matrix completion by exploiting the low-rank constraint.
In~\cite{Bonnabel2011}, a linear regression algorithm is proposed, where the parameter of this algorithm is a fixed-rank matrix based on the Riemannian manifold geometry.
In~\cite{Mishra2012}, the authors propose a quotient geometric matrix completion method.
The authors in~\cite{grouse2010Balzano} propose an online algorithm for tracking subspaces, Grassmannian rank-one update subspace estimation.
In~\cite{ngonips2012scaled}, a gradient methods based on scaled metric on the Grassmann manifold is proposed.
The authors in~\cite{Wen2012} propose a low-rank matrix fitting algorithm to solve large scale matrix completion problems by exploiting nonlinear successive over-relaxation.
In~\cite{RechtNIPS2011hogwild}, a lock-free approach to parallelizing stochastic gradient descent is proposed.
However, all these matrix factorization methods only consider the general least square loss, which cannot be directly applied to handle $\ell_{1,2}$ loss.
\yanred{
Moreover, \cite{jain2013low} can also be used for matrix completion based on alternating minimization,
but they require the incoherent matrix assumption and a fresh measurements at each iteration.
Thus their method can not be guaranteed to converge the global solution in our work.
In addition, as shown in \cite{vandereycken2013lowrank}, the Riemannian manifold method converges faster than the alternating minimization approach.
}

Some other fusion algorithms are proposed for specific tasks, which would be hard to extend to general problems.
In~\cite{zheng2015query}, the authors estimate a feature’s effectiveness in a query-adaptive manner for image retrieval problems,
and they combine the scores of multiple features weighted by their effectiveness.
In~\cite{zha2015exploiting}, they use fusion features scores of different CNN layers and encoded features improve the accuracy of action recognition.
In~\cite{feichtenhofer2016convolutional}, the authors explore a variety of fusion methods to combine spatial and temporal CNN models, significantly improving the performance of two-stream network~\cite{simonyan2014two}.
\cite{wangmodality} proposes a framework use high-dimensional Fisher Vector features from RGB, HHA and surface normal modalities to effectively achieve state-of-the-art scene classification performance.
\cite{Wang_Transformation,tapaswi2015movieqa,yaohighlight} use some simple strategies to choose specific weight for different scores from multiple features.

@@

Suppose there are $n$ testing instances and $\calC$ classes.
We denote each instance as $x_i \in \dsR^{d}$ where $1 \leq i \leq n$.
Assume that we have already trained $m$ classifiers, \ie. $f_1, f_2, ... f_m$.
Then by applying each single classifier $f_j$ ($1 \leq j \leq m$) on the entire testing data, one can derive an indicator matrix $\bL_j \in \dsR^{n \times \calC}$, where $\bL_{j, ic} = 1$ if the $i$-th instance is assigned to the $c$ class, otherwise $\bL_{j, ic} = 0$ (as shown in Figure~\ref{fig:framework}).
Let $\bL = [ \bL_1, \bL_2, ..., \bL_m ]$.
%%On one hand, we aim to preserve the consistency among $m$ classifiers, so we introduce a rank-$m$ constraint on $\bL$.
On one hand, we aim to preserve the consistency among $m$ classifiers, so we introduce a rank constraint on $\bL$.
On the other hand, to catch the outlier columns, we apply robust $\ell_{1, 2}$ loss, which is computed by
{\small
\begin{align}
|| \bX ||_{1,2} = \sum_{j = 1}^{m\calC} \sqrt{ \sum_{i = 1}^{n} \bX_{ij}^2 }
\end{align}
}
\noindent
Thus, the proposed model can be written as below:
{\small
\begin{align}\label{eq:l12_rankconstraint}
  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}~~~~~~\st~~\rank(\bX) = p
\end{align}
}
\noindent
where $\bX \in \dsR^{n \times m\calC}$ is the underlying low-rank label matrix to be recovered, $\rank(\bX)$ obtains the rank of $\bX$,
and $p$ is a scalar.
In our setting, to preserve the consistency among various classifiers, we set $p = \calC$.

It is difficult to optimize Problem~(\ref{eq:l12_rankconstraint}) directly due to the presence of the rank constraint.
We hence transform the original problem as a matrix factorization formulation as below:
{\small
\begin{align}\label{eq:l12_mf}
  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}   \nonumber \\
         \st ~&~ \bX = \bU \bV,~\bU \in \dsR^{n \times p},~\bV \in \dsR^{p \times m\calC}  .
\end{align}
}
\noindent
Nevertheless, existing matrix factorization algorithms focus on smooth loss functions, rather than a non-smooth $\ell_{1,2}$ loss function~\cite{tanicml2014riemannian,vandereycken2013lowrank,Wen2012,ngonips2012scaled,rtrmc2011boumal}.
In the following section, we present an ALM optimization framework to solve Problem~(\ref{eq:l12_mf}).

@@

  \STATE 3: $\blambda_{t+1} = \blambda_{t} + \mu_{t} (\bL - \bX_{t+1} - \bE_{t+1})$.

@@

By introducing a new variable $\bE = \bL - \bX$, we can develop Problem~(\ref{eq:l12_mf}) as below:
{\small
\begin{align}\label{eq:mf_l21_constrained}
  \min_{\bE, \bX} ~&~ || \bE ||_{1,2}      \nonumber \\
  \st             ~&~ \bE = \bL - \bX  ,   \nonumber \\
                  ~&~ \bX = \bU \bV,~\bU \in \dsR^{n \times p},~\bV \in \dsR^{p \times m \calC}
\end{align}
}
\noindent 
The augmented Lagrangian function of Problem~(\ref{eq:l12_mf}) is constructed as below
{\small
\begin{align}\label{eq:lagrangian_l21}
  \calL (\bX, \bE, \blambda, \mu) = &~ || \bE ||_{1,2} + \langle \blambda, \bL - \bX - \bE \rangle      \nonumber \\
                                    & + \frac{\mu}{2} || \bL - \bX - \bE ||_F^2
\end{align}
}
\noindent
where $\bX = \bU \bV$, $\mu$ is a scalar,
and $\blambda \in \dsR^{n \times m\calC}$ are the Lagrangian multipliers.
Here $\langle \bA, \bB \rangle$ is the inner product of $\bA \in \dsR^{m \times n}$ and $\bB \in \dsR^{m \times n}$, and defined as $\langle \bA, \bB \rangle = \sum_{i=1}^{n} \sum_{j=1}^{m} \bA_{ij} \bB_{ij}$.
Then we can update $\bX$ and $\bE$ alternatively, which is summarized in Algorithm~\ref{alg:alm_mf}.

\yanred{
The previous ALM methods~\cite{liu2013robust} usually focus on the convex problem,
but Problem~(\ref{eq:l12_mf}) is the non-convex problem.
In addition, we proof the convergence of ALM for solving a non-convex problem relying on the gradient,
rather than the (xxxxxxxx) for convex problem,
as following:
}

\yanred{
\begin{theorem}
\label{theorem:alm_convergence}
  Suppose the sequences $\{\bX_k\}_{k=1}^{\infty}$, $\{\bE_k\}_{k=1}^{\infty}$ and $\{\blambda_k\}_{k=1}^{\infty}$ are generated by Algorithm~\ref{alg:alm_mf},
  and $\{\blambda_k\}$ is bounded.
  As $k \to \infty$, the gradient of $\calL$ vanishes,
  thus any accumulation point $(\bX^*, \bE^*)$ is a stationary point.
\end{theorem}
}

\begin{proof}
\label{proof:proof_AA}
  The proof can be found in Appendix A.
\end{proof}

\subsection{Optimization of The Subproblem of $\bX$}

Particularly, to update $\bX$, we have the following augmented Lagrangian function \wrt. $\bX$:
{\small
\begin{align}\label{eq:langrangian_wrt_X}
  \calL (\bX) = & \langle \blambda, \bL - \bX - \bE \rangle + \frac{\mu}{2} || \bL - \bX - \bE ||_F^2  \nonumber  \\
              = & \frac{\mu}{2} || \bM - \bX ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
\end{align}
}
\noindent
where $\bM = \bL - \bE + \frac{\blambda}{\mu}$.
Hence, we derive the following subproblem \wrt. $\bX$:
{\small
\begin{align}\label{eq:subproblem_wrt_X}
  \min_{\bX} ~&~ || \bM - \bX ||_F^2    \nonumber \\
  \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{n \times p},~\bV \in \dsR^{p \times m\calC}   .
\end{align}
}
\noindent
%Problem~(\ref{eq:subproblem_wrt_X}) contains a smooth loss function \wrt. $\bX$, thus can be efficiently solved by existing fixed-rank matrix factorization optimization algorithms, such as LRGeomCG~\cite{vandereycken2013lowrank}.
Problem~(\ref{eq:subproblem_wrt_X}) contains a smooth loss function of $\bX$.
We thus propose to solve the subproblem by exploiting Riemannian geometry of smooth fixed-rank matrices, which is briefly presented below.

>>>>

\newcommand\mycomment[1]{}

\def\ranksym{p}
\def\symp{r}

\def\calP{\mathcal{P}}
\def\M{\mathcal{M}}
\def\R{{\mathbb R}}
\def\bR{{\bf R}}
\def\U{{\bf U}}
\def\V{{\bf V}}
\def\diag{\mbox{diag}}
\def\bsigma{\mbox{{\boldmath $\sigma$}}}
\def\trsp{{\sf T}}
\def\I{{\bf I}}
\def\0{{\bf 0}}
\def\G{{\bf G}}
\def\grad{{\text{grad}}}
\def\bZ{{\bf Z}}
\def\bfeta{\mbox{{\boldmath $\eta$}}}
\def\mT{{\mathcal T}}

@@

\def\yanred{\textcolor{black}}
\def\yanblue{\textcolor{blue}}
\def\kuired{\textcolor{red}}
%%%%%

@@

\begin{abstract}
In many real-world applications, data can be represented by multiple ways or multi-view features, in order to describe various characteristics of data.
In this sense, the prediction performance can be significantly improved by taking advantages of these features together.
Late fusion, which combines the predictions of multiple features, is a commonly used approach to make the final decision for a test instance.
However, it is ubiquitous that different features dispute the prediction on the same data with each other, leading to  performance degeneration.
%Therefore, outlier detection is crucial when combining the predictions of different features.
In this paper, we propose an efficient and effective matrix factorization-based approach to fuse predictions from multiple sources,
aiming to avoid the performance degeneration caused by the controversy of multiple features. In this way, the consistency of results by various features can be preserved, which can relieve the performance degeneration.
Extensive experiments demonstrate efficacy of the proposed method on outlier detection and performance improvement,
which outperforms the previous state-of-the-art late fusion algorithms on most datasets.

@@

%% late fusion is a common single model -> single feature, 介绍late fusion
Late fusion, a typical approach to obtaining the final decision on testing data, aims to fuse the predictions from different features~\cite{ye2012robust,xuiccv2013feature,lai2015learning,vanicassp2014late}.
A commonly used method is to learn weights for predictions from various features to combine them, which has a number of variations~\cite{gehler2009feature,xuiccv2013feature,lai2015learning}.
Among these algorithms, multiple kernel learning (MKL)~\cite{lanckriet2004learning,Rakotomamonjy2008Simplemkl} is often used to train such a weighted combination.
However, a single feature may produce corrupted predictions on some data, which likely degenerates performance.
To deal with this issue, therefore, some works formulate it as a robust low-rank matrix recovery problem~\cite{gaoijcai2016robust,ye2012robust} by nuclear norm minimization.
Nevertheless, nuclear norm minimization applied in these works requires singular value decompositions (SVDs), which would be computationally unaffordable for large matrices.

\begin{figure}[!t]
\begin{center}
\includegraphics[width=0.46\textwidth]{resource/frame_work.pdf}
\end{center}
\caption{Framework of our late fusion algorithm.
In this example, there are 10 instances 3 classifiers and 3 classes.
Predictions of each classifier are converted to a binary indicator matrix,
denoted by $L_1$, $L_2$ and $L_3$.
Let $L = [L_1, L_2, L_3]$ be the label matrix.
Our algorithm detects and removes the outliers on $L$ and then recover the underlying low-rank subspace of $L$ as the prediction for testing instances.
We finally apply a post-processing method to generate the fused results.
%First, there are $\calC=3$ classifiers' results for $n=10$ instances.
%Each of them are converted into ``binary'' indicators from the soft prediction results, as $L = [L_1, L_2, L_3]$.
%Then, our ALM-based optimization process the binary indicator matrix into a recovered matrix $X$,
%which can be treated as soft prediction scores for testing instances.
%Finally, the fused prediction results are generated by a post-processing method.
}
\label{fig:framework}
\end{figure}

To avoid the expensive nuclear norm minimization,
in this paper, we propose a more efficient matrix factorization algorithm to recover the underlying low-rank label matrix.
Particularly, our method searches the solution in a low-rank subspace under a fixed-rank constraint.
This is a hard constraint, and it is different from~\cite{gaoijcai2016robust,ye2012robust} which introduce a soft constraint on the low-rank property.
On the other hand, to remove the abnormal predictions generated by individual features, we propose to filter out these inconsistent results by using the $\ell_{1,2}$ regularization (See Fig.\ref{fig:framework}.
Notations are introduced shortly.).
\yanred{
Specially, $\ell_{1,2}$ loss preserves the fidelity within each column by $\ell_{2}$ loss in the vertical direction and is robust to sparse errors across all the columns by $\ell_{1}$ loss in the horizontal direction.
Compared to $\ell_{1,2}$ loss, $\ell_{2}$ loss is sensitive to outliers, so that may not produce robust and satisfactory predictions.
$\ell_{1}$ loss is not sensitive to outliers, but not capable to detect the abnormal features which generate corrupted results.
}
In addition, most existing matrix factorization optimization methods only consider smooth loss functions, rather than the non-smooth loss.
Thus, we in particular present an approach based on augmented Lagrangian multiplier (ALM) to extend matrix factorization methods to non-smooth problems.

The main contributions of this work are summarized as follows:
\begin{itemize}
  \item We formulate the late fusion problem as a fixed-rank robust matrix recovery problem, which is the first attempt to introduce a hard constraint on the low-rank property to the late fusion problem.
      Our model intuitively removes inconsistent predictions made by abnormal features and preserves the consistency of predictions from different sources.
  \item We propose an ALM-based algorithm to enable matrix recovery algorithms to handle non-smooth $\ell_{1,2}$ loss, rather than a simple least square loss which has been frequently studied in literature.
  %\item Our proposed algorithm is more efficient than most state-of-the-art late fusion methods.
  %It is capable of handling large scale problems.
  \item We provide theoretical convergence analysis for the proposed robust matrix recovery algorithm.
  \item Empirical studies show significantly improvement of our proposed method compared to existing late fusion algorithms.
\end{itemize}

@@

%MKL based method is a simple but efficient way to combine different features for multi-model fusion,
%and many improved algorithms have been proposed by introducing more constraint, boosting methods and other optimization.
MKL is a common way to combine different features for multi-model fusion.
In~\cite{vedaldi2009multiple}, the authors use MKL to learn an optimal combination of exponential ${\chi}^2$ kernels capturing a different feature channel.
Gehler \etal \cite{gehler2009feature} propose boosting approaches to ensemble different features, which learns the correct weighting of multiple predicted confidence scores from different models.
The authors of \cite{natarajan2012multimodal} propose a two-step strategy employing MKL and late score fusion methods to combine diverse features, specifically on event detection tasks.
In~\cite{lai2015learning}, a sample specific late fusion based on graph Laplacian with RankSVM style constraints is proposed,
which learns sample specific fusion weights by diffusing the information from labeled samples to the unlabeled one.
Xu \etal \cite{xuiccv2013feature} propose an optimization algorithm to combine diverse decision values,
which learns the weights, thresholding and smoothing parameters in a joint framework.
However, all these MKL based fusion methods or others only learn weights to combine different basic models, which do not consider the outlier rejection in the fusion process specifically.

%Our proposed late fusion algorithm is based on matrix factorization,
%which has attracted increasing attention recently.
Matrix factorization has attracted increasing attention recently.
Many manifold optimization algorithms on matrix factorization have been proposed by exploiting the manifold geometry in a subspace.
Based on manifold optimization, fixed-rank matrices are supposed to belong to a smooth matrix manifold~\cite{Absil2008OAMM,vandereycken2013lowrank,rtrmc2011boumal,Bonnabel2011,Mishra2012,ngonips2012scaled}.
For instance, in~\cite{vandereycken2013lowrank}, the authors propose a low-rank geometric conjugate gradient (LRGeomCG) method.
In~\cite{rtrmc2011boumal}, first- and second-order Riemannian trust-region methods are applied to solve the low-rank matrix completion by exploiting the low-rank constraint.
In~\cite{Bonnabel2011}, a linear regression algorithm is proposed, where the parameter of this algorithm is a fixed-rank matrix based on the Riemannian manifold geometry.
In~\cite{Mishra2012}, the authors propose a quotient geometric matrix completion method.
%The authors in~\cite{grouse2010Balzano} propose an online algorithm for tracking subspaces, Grassmannian rank-one update subspace estimation.
In~\cite{ngonips2012scaled}, a gradient methods based on scaled metric on the Grassmann manifold is proposed.
The authors in~\cite{Wen2012} propose a low-rank matrix fitting algorithm to solve large scale matrix completion problems by exploiting nonlinear successive over-relaxation.
In~\cite{RechtNIPS2011hogwild}, a lock-free approach to parallelizing stochastic gradient descent is proposed.
In \cite{jain2013low} the authors propose a alternating minimization method for matrix factorization with a global optimality guarantee,
but they require the incoherent matrix assumption and a fresh measurements at each iteration.
Thus their method cannot be guaranteed the global optimality in our work.
In addition, as shown in \cite{vandereycken2013lowrank}, the Riemannian manifold method may converge faster than the alternating minimization approach.
However, most existing matrix factorization methods only consider the general least square loss, which cannot be directly applied to handle $\ell_{1,2}$ loss.

Some other fusion algorithms are proposed for specific tasks.
The authors of \cite{zheng2015query} estimate a feature’s effectiveness in a query-adaptive manner for image retrieval problems,
and they combine the scores of multiple features weighted by their effectiveness.
Zha \etal \cite{zha2015exploiting} use fusion features scores of different CNN layers and encoded features improve the accuracy of action recognition.
In~\cite{feichtenhofer2016convolutional}, the authors explore a variety of fusion methods to combine spatial and temporal CNN models, significantly improving the performance of two-stream network~\cite{simonyan2014two}.
\cite{wangmodality} proposes a framework use high-dimensional Fisher Vector features from RGB, HHA and surface normal modalities to effectively achieve state-of-the-art scene classification performance.
\cite{Wang_Transformation,tapaswi2015movieqa,yaohighlight} use some simple strategies to choose specific weight for different scores from multiple features.
The authors in~\cite{vanicassp2014late} point out that missing values in predictions can be a challenge for late fusion due to the absence of features.
These special designed fusion algorithms can be hard to extend to general problems, being lack of generalization.

@@

Suppose there are $n$ testing instances and $\calC$ classes.
We denote each instance as $x_i \in \dsR^{d}$ where $1 \leq i \leq n$.
Assume that we have already trained $m$ classifiers, \ie. $f_1, f_2, ... f_m$.
Then by applying each single classifier $f_j$ ($1 \leq j \leq m$) on the entire testing data, one can derive an indicator matrix $\bL_j \in \dsR^{n \times \calC}$, where $\bL_{j, ic} = 1$ if the $i$-th instance is assigned to the $c$ class, otherwise $\bL_{j, ic} = 0$ (as shown in Figure~\ref{fig:framework}).
Let $\bL = [ \bL_1, \bL_2, ..., \bL_m ]$.
%%On one hand, we aim to preserve the consistency among $m$ classifiers, so we introduce a rank-$m$ constraint on $\bL$.
On one hand, we aim to preserve the consistency among $m$ classifiers, so we introduce a rank constraint on $\bL$.
On the other hand, to catch the outlier columns, we apply robust $\ell_{1, 2}$ loss, which is computed by
$
|| \bX ||_{1,2} = \sum_{j = 1}^{m\calC} \sqrt{ \sum_{i = 1}^{n} \bX_{ij}^2 }  .
$
Thus, a general formulation of recovering the underlying low-rank label matrix can be written as follows:
{
\begin{align}\label{eq:l12_rankconstraint}
  \min_{\bX} ~&~ || \calP_{\Omega} (\bL - \bX) ||_{1,2}~~~~~~\st~~\rank(\bX) = p
\end{align}
}
\noindent
where $\bX \in \dsR^{n \times m\calC}$ is the underlying low-rank label matrix to be recovered, $\rank(\bX)$ obtains the rank of $\bX$,
$\Omega$ denotes a subset containing the indices of the observed entries,
and $p$ is a scalar.
Here $\calP_{\Omega}$ denotes the orthogonal projection onto the linear space of matrices support on $\Omega: \calP_{\Omega}(\bX) = \bX_{ij}$ if $(ij) \in \Omega$; $\calP_{\Omega} = 0$ otherwise.
This includes some cases where missing elements may occur~\cite{vanicassp2014late}.
In our setting, to preserve the consistency among various classifiers, we set the hard constraint of the rank, \ie, $p = \calC$.

It is difficult to optimize Problem~(\ref{eq:l12_rankconstraint}) directly due to the presence of the rank constraint.
We hence transform the original problem as a matrix factorization formulation as follows:
{
\begin{align}\label{eq:l12_mf}
  \min_{\bX} || \calP_{\Omega}(\bL - \bX) ||_{1,2} ,~  \st~ \rank(\bX) = p  .
\end{align}
}
\noindent
Nevertheless, existing matrix factorization algorithms focus on smooth loss functions, rather than a non-smooth $\ell_{1,2}$ loss function~\cite{tanicml2014riemannian,vandereycken2013lowrank,Wen2012,ngonips2012scaled,rtrmc2011boumal}.
In the following section, we present an ALM optimization framework to solve Problem~(\ref{eq:l12_mf}).

@@

  \STATE 3: $\blambda_{t+1} = \blambda_{t} + \mu_{t} (\calP_{\Omega}{(\bL - \bX_{t+1} - \bE_{t+1})})$.

@@

By introducing a new variable $\calP_{\Omega} (\bE) = \calP_{\Omega} (\bL - \bX)$, we can develop Problem~(\ref{eq:l12_mf}) as below:
{
\begin{align}\label{eq:mf_l21_constrained}
  \min_{\bE, \bX} ~&~ || \bE ||_{1,2}      \nonumber \\
  \st             ~&~ \calP_{\Omega} (\bE) = \calP_{\Omega} (\bL - \bX)  ,~ \rank(\bX) = p  .
\end{align}
}
\noindent
The augmented Lagrangian function of Problem~(\ref{eq:l12_mf}) is constructed as below
{
\begin{align}\label{eq:lagrangian_l21}
  \calL (\bX, \bE, \blambda, \mu) = &~ || \bE ||_{1,2} + \langle \blambda, \calP_{\Omega} (\bL - \bX - \bE) \rangle      \nonumber \\
                                    & + \frac{\mu}{2} || \calP_{\Omega} (\bL - \bX - \bE) ||_F^2
\end{align}
}
\noindent
where $\rank (\bX) = p$, $\mu$ is a scalar,
and $\blambda \in \dsR^{n \times m\calC}$ are the Lagrangian multipliers.
Here $\langle \bA, \bB \rangle$ is the inner product of $\bA \in \dsR^{m \times n}$ and $\bB \in \dsR^{m \times n}$, and defined as $\langle \bA, \bB \rangle = \sum_{i=1}^{n} \sum_{j=1}^{m} \bA_{ij} \bB_{ij}$.
Then we can update $\bX$ and $\bE$ alternatively, which is summarized in Algorithm~\ref{alg:alm_mf}.
The following lemma and theorem provide the theoretical convergence guarantee of the proposed algorithm.
We emphasize that our problem is a non-convex problem with a rank constraint, which is rarely studied in previous literatures.

\begin{lemma}
Given that the sequence $\{ \mu_{t} \}$ is always increasing, $\mu_{0} > 0$ and $\blambda_{0} = 0$, the sequence $\{ \blambda_{t} \}$ computed by Algorithm~\ref{alg:alm_mf} is bounded.
\end{lemma}

\begin{proof}
  The proof can be found in Appendix A.
  \mycomment{
  By the optimality of $\bE_{t+1}$ in Step 2 in Algorithm~\ref{alg:alm_mf}, we have the sub-differential of $\calL$ w.r.t. $\bE$ as zeros:
  {
  \begin{align}
  \label{eq:derivatives_calL_E}
    0 & \in \frac{\calL(\bX_{t+1}, \bE_{t}, \blambda_{t}, \mu_{t})}{\bE_{t+1}} \nonumber \\
      & = \partial(|| \bE_{t+1} ||_{1,2}) + \blambda_{t} + \mu_{t} (\calP_{\Omega} (\bL - \bX_{t+1} - \bE_{t+1})) \nonumber \\
      & = \partial(|| \bE_{t+1} ||_{1,2}) + \blambda_{t+1}   \nonumber \\
    \Rightarrow & -\blambda_{t+1} \in \partial(|| \bE_{t+1} ||_{1,2})  .
  \end{align}
  }
  \noindent
  Consider the computation of $\bE_{t+1}$ in Eq~(\ref{eq:column_wise_soft_thresholding}), which is associated with $\bL, \bX_{t+1}$, $\blambda_{t}$ and $\mu_{t}$.
  $\bL$ is the observation and thus bounded.
  $\bX_{t+1}$ is bounded due to the convergence guarantee of Step 1 in Algorithm~\ref{alg:alm_mf}~\cite{vandereycken2013lowrank}.
  $\{ \blambda_{t} \}$ is initialized by setting $\blambda_{0} = 0$ and $\{ \mu_{t} \}$ is non-decreasing.
  Thus when updating by Algorithm~\ref{alg:alm_mf}, $\bE_{t+1}$, $\partial(\bE_{t+1})$ and $\blambda_{t}$ are all bounded accordingly as $t$ increases.
  This completes the proof.
  }
\end{proof}

\begin{theorem}
\label{theorem:alm_convergence}
  Suppose the sequences $\{\bX_k\}_{k=1}^{\infty}$, $\{\bE_k\}_{k=1}^{\infty}$ and $\{\blambda_k\}_{k=1}^{\infty}$ are generated by Algorithm~\ref{alg:alm_mf}.
  As $k \to \infty$, the gradients of $\calL$ w.r.t. $\bX$ and $\bE$ vanish,
  thus any accumulation point $(\bX^*, \bE^*)$ is a stationary point.
\end{theorem}

%\vspace{1cm}
\begin{proof}
\label{proof:proof_AA}
  The proof can be found in Appendix B.
\end{proof}

\subsection{Subproblem Optimization w.r.t. $\bX$}

To update $\bX$, we have the following augmented Lagrangian function \wrt. $\bX$:
{
\begin{align}\label{eq:langrangian_wrt_X}
  \calL (\bX) = & \langle \blambda, \calP_{\Omega} (\bL - \bX - \bE) \rangle + \frac{\mu}{2} || \calP_{\Omega} (\bL - \bX - \bE) ||_F^2  \nonumber  \\
              = & \frac{\mu}{2} || \calP_{\Omega} (\bM - \bX) ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
\end{align}
}
\noindent
where $\bM = \bL - \bE + \frac{\blambda}{\mu}$.
Hence, we derive the following subproblem \wrt. $\bX$:
{
\begin{align}\label{eq:subproblem_wrt_X}
  \min_{\bX} || \calP_{\Omega} (\bM - \bX) ||_F^2,~ \st~ \rank(\bX) = p.
\end{align}
}
\noindent
%Problem~(\ref{eq:subproblem_wrt_X}) contains a smooth loss function \wrt. $\bX$, thus can be efficiently solved by existing fixed-rank matrix factorization optimization algorithms, such as LRGeomCG~\cite{vandereycken2013lowrank}.
Problem~(\ref{eq:subproblem_wrt_X}) contains a smooth loss function of $\bX$.
We thus propose to solve the subproblem by exploiting Riemannian geometry of smooth fixed-rank matrices, which is briefly presented below.
